Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-07-26 supp.rnw
Add model fit and partial residual plots to the supplementary material.

>>>>

%TODO: x and y axis labels.
<<echo=FALSE>>=
	model_fit_plot <- function(parameters) {
		plot_df <- data.frame(
			observed = input_data$response_vector,
			fitted = input_data$get_fitted_values(parameters),
			focal = species_dat$name[input_data$focal_vector]
		)
		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal)
		return(plot)
	}

	partial_residuals_plot <- function(parameters) {
		#TODO: Give species names on facet plot labels.
		plot_df <- c()
		for(row_index in 1:num_species) {
			for(col_index in 1:num_species) {
				temp_df <- data.frame(
					y = input_data$get_partial_residuals(parameters, row_index, col_index),
					x = input_data$get_partial_residuals_x(row_index, col_index)
				)
				temp_df$row_index <- rep(row_index, nrow(temp_df))
				temp_df$col_index <- rep(col_index, nrow(temp_df))
				plot_df <- rbind(plot_df, temp_df)
			}
		}

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::facet_grid(row_index~col_index)
		return(plot)
	}

	best_parameters <- brute_data$parameters[[which.max(brute_data$statistics[[ic_weight]])]]
	average_parameters <- brute_data$average_parameters
@

%TODO: Reorder partial residual/model fit plots to use same species order as other figures.
%TODO: Add "S" to figure numbers.
\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(best_parameters))
	@

	\caption{%
		Plot of model fit using the most parsimonious model.
	}
	\label{fig:model-fit-best}
\end{figure}

\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(average_parameters))
	@

	\caption{%
		Plot of model fit using the model average model.
	}
	\label{fig:model-fit-average}
\end{figure}

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residuals_plot(best_parameters))
	@

	\caption{%
		Partial residuals plot using the most parsimonious model.
	}
	\label{fig:partial-residual-best}
\end{figure}

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residuals_plot(average_parameters))
	@

	\caption{%
		Partial residuals plot using the model average model.
	}
	\label{fig:partial-residual-average}
\end{figure}
